COG-ED Manuscript

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
finished loop for SCA (BF10 still missing tho)

  # Here we repeat the multi level model with all analysis pipelines.

@@

    # intra-class-correlation

    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])

@@

>>>>

  # here we repeat the multi level model with all analysis pipelines

  sca_results <- data.frame(pipeline = character(), beta_level = double(), p_level = double(),
                            beta_nfc = double(), p_nfc = double())

@@

    # random slopes model

    m1_sca <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
                   data = sca_data, REML = T)

    # combine current results and the bigger data frame

    newdata <- data.frame(pipeline = names(pipelines_data[i]),
                          beta_level = summary(m1_sca)$coefficients[2,1],
                          p_level = summary(m1_sca)$coefficients[2,5],
                          beta_nfc = summary(m1_sca)$coefficients[3,1],
                          p_nfc = summary(m1_sca)$coefficients[3,5])
    sca_results <- rbind(sca_results, newdata)

@@

```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

  # sort the data frame by the fixed effects estimate of the predictor 'level'

  sca_results <- sca_results[order(beta_level), ]
